Empirical Evaluation of eval in R

### 2020-09-14 inst/analysis/analysis_stable.Rmd
Updates

```{r subsample_for_ast}
#ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
ast_sizes <- read_fst(path(RUN_DIR, "package-evals-traced.3/summarized-ast-size.fst")) %>% as_tibble() %>% 
      filter(eval_source_type != "<undefined>") %>% 
      rename(dataset = eval_source_type)
```

@@

```{r env_assign}
eval_calls_env_assign <- eval_calls %>% filter(!is.na(expr_resolved)) %>% mutate(env_assign = pblapply(expr_resolved, is_assign_str, cl = parallel::detectCores() - 2))

#eval_calls_env_assign2 <-  eval_calls_env_assign %>% filter(is.logical(env_assign)) %>% hoist("env_assign", env_assign = 1)
```

>>>>

```{r subsample_for_ast}
#ast_sizes <- eval_calls %>% slice_sample(n=10000) %>% mutate(expr_resolved_nodes = map_int(expr_resolved, expr_size_str))
# Now precomputed during the tracing
#ast_sizes <- read_fst(path(RUN_DIR, "package-evals-traced.3/summarized-ast-size.fst")) %>% as_tibble() %>% 
#      filter(eval_source_type != "<undefined>") %>% 
#      rename(dataset = eval_source_type)

ast_sizes <- eval_calls 
```

@@

```{r display_frequent_env_core}
classified_envir_core <- classified_envir %>% filter(dataset == "core") %>% add_count(env_class, wt=nb_ev_calls, sort = TRUE) %>% group_by(env_class)  %>% slice_max(order_by = nb_ev_calls, n = 10) %>% ungroup()

classified_envir_core %>% select(env_class, eval_call_expression, eval_call_srcref, caller_expression, n) %>% distinct() %>% datatable()
```

```{r display_frequent_env_packages}
classified_envir_packages <- classified_envir %>% filter(dataset == "packages") %>% add_count(env_class, wt=nb_ev_calls, sort = TRUE) %>% group_by(env_class)  %>% slice_max(order_by = nb_ev_calls, n = 10) %>% ungroup()

classified_envir_packages %>% select(env_class, eval_call_expression, eval_call_srcref, caller_expression, n) %>% distinct() %>% datatable()
```
